Output Summary

### 2021-07-23 03-post-process/output-plots.Rmd

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "gamma",
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
  "^phi_M_O1", "^phi_O1_O2", "^phi_O2_O3",
  "^psi_O1_Rb", "^psi_O2_Rb", "O_phi_scaler_nat_hat"
)

@@

```{r survival-data-fits, fig.width = 5, fig.height = 6}
par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = TeX("$Summer\\,Parr \\rightarrow LGR"))
plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = TeX("$Fall\\,Parr \\rightarrow LGR"))
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(NOR)"))
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(HOR)"))
plot_tseries(post_summ(post, "^phi_Ma_M[.+,1]$"), expit(jags_data$Lphi_obs_Ma_M[observable,1]), main = TeX("$LGR\\,Smolt \\rightarrow BON\\,(NOR)"))
plot_tseries(post_summ(post, "^phi_Ma_M[.+,2]$"), expit(jags_data$Lphi_obs_Ma_M[observable,2]), main = TeX("$LGR\\,Smolt \\rightarrow BON\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

    # give names
    dimnames(Ra) = dimnames(jags_data$n_broodstock)
    dimnames(Ma) = dimnames(jags_data$Mb_obs)

@@

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "phi_M_O1[.+,1]$"), main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_M_O1[.+,2]$"), main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = 0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Survival")
```

@@

```{r sex-plots, fig.width = 7, fig.height = 4}
par(mfrow = c(1,2), oma = c(1,1,0,0))
plot_tseries(post_summ(post, "^omega[.+,1,1]$"), main = "Natural Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^omega[.+,1,2]$"), main = "Hatchery Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Female Proportion of Esutary Smolts")
```

@@

* `mu_omega[1]`: mean probability of being a female at ocean entry
* `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types, different for origin types)
* `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)
* `mu_pi[1]`: mean probability of becoming a fall migrant LH type at end of summer
* `mu_psi_O1_Rb`: mean probability of maturing at age 3 given survived to that point (`[1]`: females, `[2]`: males)
* `mu_psi_O2_Rb`: mean probability of maturing at age 4 given did not mature at age 3 and survived to that point (`[1]`: females, `[2]`: males)

>>>>

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "gamma",
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
  "^phi_O0_O1", "^phi_O1_O2", "^phi_O2_O3",
  "^psi_O1_Rb", "^psi_O2_Rb", "O_phi_scaler_nat_hat"
)

@@

```{r survival-data-fits, fig.width = 5, fig.height = 6}
par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = TeX("$Summer\\,Parr \\rightarrow LGR"))
plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = TeX("$Fall\\,Parr \\rightarrow LGR"))
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(NOR)"))
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(HOR)"))
plot_tseries(post_summ(post, "^phi_Ma_O0[.+,1]$"), expit(jags_data$Lphi_obs_Ma_O0[observable,1]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,(NOR)"))
plot_tseries(post_summ(post, "^phi_Ma_O0[.+,2]$"), expit(jags_data$Lphi_obs_Ma_O0[observable,2]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

    # give names
    dimnames(Ra) = dimnames(jags_data$n_remove)
    dimnames(Ma) = dimnames(jags_data$Mb_obs)

@@

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "phi_O0_O1[.+,1]$"), main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O0_O1[.+,2]$"), main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = 0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Survival")
```

@@

```{r sex-plots, fig.width = 7, fig.height = 4}
par(mfrow = c(1,2), oma = c(1,1,0,0))
plot_tseries(post_summ(post, "^omega[.+,1,1]$"), main = "Natural Origin", yrs = as.numeric(rownames
                                                                                           (jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^omega[.+,1,2]$"), main = "Hatchery Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Female Proportion of Esutary Smolts")
```

@@

* `mu_omega[1]`: mean probability of being a female at ocean entry
* `mu_phi_Ma_O0`: mean probability of surviving from LGD to ocean entry
* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types, different for origin types)
* `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)
* `mu_pi[1]`: mean probability of becoming a fall migrant LH type at end of summer
* `mu_psi_O1_Rb`: mean probability of maturing at age 3 given survived to that point (`[1]`: females, `[2]`: males)
* `mu_psi_O2_Rb`: mean probability of maturing at age 4 given did not mature at age 3 and survived to that point (`[1]`: females, `[2]`: males)
